PK object batch mode trial

### 2023-06-28 data-raw/batchMode_trial_gpm.Rmd
Fixed function call for facetting and added a prediction value limiter when plotting model fits

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5034773",
                                                                   "DTXSID5032600",
                                                                   "DTXSID7022253"))
```

@@

devtools::load_all()
my_plot <- plot(my_pk, use_scale_conc = FALSE)
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)

# This is printable into a one file, multipage pdf
pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_OnefileTest.pdf",
    width = 10,
    height = 8)
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)
dev.off()

>>>>

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5032600",
                                                                   "DTXSID7022253"))
```

@@

devtools::load_all()
my_plot <- plot(my_pk, use_scale_conc = TRUE)
plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE)

# This is printable into a one file, multipage pdf
pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_freeY.pdf",
    width = 10,
    height = 8)
plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE)
dev.off()
